SNP-harmonization

### 2021-03-25 analysis/SNP-harmonization.Rmd
snp harmonization notes

@@

cat("number of eQTLs on chromosome ", i,  "(by lasso, shared with UKB) that match after flip: ",
sum(a[!(a$id %in% b$id), 5] != a[!(a$id %in% b$id), 8]))
```

>>>>

eQTL information were obtained from FUSION pre-trained models. We used all SNPs with weights != 0 in

@@

cat("number of eQTLs on chromosome ", i,  "(by lasso, shared with UKB) that match after flip: ",
sum(a[!(a$id %in% b$id), 5] != a[!(a$id %in% b$id), 8]))

cat("number of eQTLs on chromosome ", i,  "(by lasso, shared with UKB) that are strand ambiguous: ",
nrow(a[(a$alt=="A" & a$ref=="T") | (a$alt=="T" & a$ref=="A") | (a$alt=="C" & a$ref=="G") | (a$alt=="G" & a$ref=="C"),]))
```
